[dcpo_demsupport]

### 2020-07-30 paper/dcpo_demsupport.Rmd
use better fix for new as_tibble()

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~make.names(., unique = TRUE)) %>% 
    rename_with(~ ls_country, .cols = everything()) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})

>>>>

df_theta <- purrr::map(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>% 
    as_tibble(.name_repair = ~ls_country) %>% 
    mutate(year = first_year + row_number() - 1) %>% 
    pivot_longer(cols = all_of(ls_country),
                 names_to = "country",
                 values_to = "theta") %>%
    arrange(country, year) %>% 
    left_join(df_controls, by = c("country", "year")) %>% 
    plm::pdata.frame(index = c("country", "year"))
})
